Understanding Supersymmetry

### 2021-09-10 alpha/SUSY/susy.tex
Add comments on SUSY vacua & illustrations

\section{Superspace \& Superfields}
	\speaker{Ban ``Bo'' Lin}\\
	\references{
	\begin{enumerate}[noitemsep,topsep=0pt,beginpenalty=10000]
	\item \textcite{Argyres:1996abc}, \S6
	\item \citetitle{Hori:2003ic} \cite{Hori:2003ic}, Chapter 12
	\end{enumerate}
	}\vspace{.5\baselineskip}

@@

	A generic superfield will give a \textit{reducible} representation of the superalgebra. To get an \textit{irreducible} representation (\textit{irrep}), we must impose a constraint on the superfield which (anti-)commutes with the superalgebra. There are two possibilities for 4D $\mcal{N} = 1$:
	\begin{enumerate}%[noitemsep]
	\item \textbf{Reality condition:} this lead to a vector multiplet. We shall revisit this in the future. For now we will proceed to the next condition, which is:

@@

	A full expansion of the Lagrangian $\mcal{L}$ (including $\mcal{K}$ and $\mcal{W}$) reveals that $F$ has no kinetic term and is quadratic in the action, thus it can be safely integrated out. The result gives us the potential for the scalar component $\phi$:
	\begin{equation}
		V(\phi,\bar{\phi})
		= g^{i\wbar{j}}
			\,\pdd{i} \mcal{W}
			\,\pdd{\wbar{j}} \wbar{\mcal{W}}
		= \abs{\pd\mcal{W}}^2
	\end{equation}
	The classical vacua satisfy $\pd_i V = 0$. 
%	Spontaneous breaking of internal symmetry happens if we have $\vev{\phi} \ne 0$. 
	On the other hand, we see that $V\ge 0$ for a positive-definite metric $g_{i\wbar{j}}$, therefore if $V = 0$ we have $\pdd{i} V = 0$ and $\pdd{i} \mcal{W} = 0$. In this case we have SUSY vacua, i.e.~SUSY is unbroken.

	In summary,
	\begin{itemize}[noitemsep]
	\item Vacua: $
		\pdd{i} V
		= \pdd{i}\,\pqty\big{\abs{\pdd{i} \mcal{W}}^2}
		= 0
	$
	\item SUSY vacua: $\pdd{i} \mcal{W} = 0$, which implies $V = 0$ thus $\pdd{i} V = 0$. 
	\end{itemize}
	Spontaneous breaking of SUSY happens if $\pdd{i} V = 0$ while $V \ne 0$, namely we don't have a SUSY vacua. 	Fig.\,1.4 of \textcite{Terning:2006bq} is a nice summary of the situations. These backgrounds will come in handy in later sections.

@@

%	\vspace{\baselineskip}
	\noindent%
	The argument of non-renormalization by Dine, Polchinski and Seiberg \cite{Seiberg:1993vc}:

@@

	\textit{Note:} in \cite{Seiberg:1993vc} Seiberg chose to call the non-renormalization in SUSY \textit{a violation of naturalness} in the conventional sense, since in the IR we see no global symmetry but we still have many vanishing amptitudes. But I believe it's okay to understand this as a new sense of naturalness, where the vanishing of amplitudes (or the rigid form of the potentials) is protected by supersymmetry and some ``hidden'' global symmetries (that are spontaneously broken in the IR).

\subsection{Why can we turn on the couplings?}
	We've argued that it's physically reasonable to turn on the coupling $\lambda$ and make it a dynamical field\footnote{
		I believe this is the so-called ``un-Higgs-ing'' procedure, and the unHiggsed field is called a ``spurion''. \\
		\hspace*{2em}
		See \https{physicsforums.com/threads/spurion-symmetry.205417}.
	}. On the other hand, as pointed out by \textcite{Argyres:1996abc}, we can simply think of this as ``just a trick''\footnote{
		See also \https{physics.stackexchange.com/q/110926/162487}. 
	}:

@@

	One concrete realization of this procedure for the $m\Phi^2$ term is given by \cite{Dine:1996ui}:
	\begin{equation}
	\begin{aligned}
		m\Phi^2
		\leadsto{}&
			M \pqty{
				\Psi - m
			}^2 + \Psi \Phi^2 \\
	\end{aligned}
	\end{equation}
	Here we've been cavaliar about constant shifts of $\mcal{W}$, as they do not affect the physics\footnote{
		On the other hand, constant shifts of $V = \abs{\pd\mcal{W}}^2$ \textit{do} matter in SUSY theories, as they are related to spontaneous SUSY breaking; see \S2 and \S4. 
	}. 
	Also, we are free to include a kinetic term for $\Psi$ in the K\"ahler potential so that it does look like a physical field. However, this does not matter much, as for $M \gg \Lambda_{\mrm{UV}}$, the $
		M \pqty{\Psi - m}^2
	$ term dominates and we always have $m \simeq \vev{\Psi}$. In the end the superpotential reduces back to $m\Phi^2$. Holomorphy of $\mcal{W}$ with respect to $m$ then follows from holomorphy with respect to $\Psi$.

@@

\section{Moduli Space of Vacua}
	\speaker{Yuan Zhong}\\
	\references{%
%	\begin{enumerate}[noitemsep,topsep=0pt]
%	\item
	\textcite{Argyres:1996abc}, \S8
%	\end{enumerate}
	}\vspace{.5\baselineskip}

>>>>

\section{Superspace \& Superfields}
	\speaker{Ban ``Bo'' Lin}\\
	\references{
	\begin{enumerate}[noitemsep,topsep=0pt,beginpenalty=10000]
	\item \textcite{Argyres:1996abc}, \S6 \& \S9
	\item \citetitle{Hori:2003ic} \cite{Hori:2003ic}, Chapter 12
	\end{enumerate}
	}\vspace{.5\baselineskip}

@@

	A generic superfield will give a \textit{reducible} representation of the superalgebra. To get an \textit{irreducible} representation (\textit{irrep}), we must impose a constraint on the superfield which (anti-)commutes with the superalgebra. There are two possibilities for 4D $\mcal{N} = 1$:
	\begin{enumerate}%[noitemsep]
	\item \textbf{Reality condition:} $\bar{V} = V$, this gives us the vector superfield; see \S10.1 of \textcite{Argyres:1996abc}. We shall revisit this in \S6. For now we will proceed to the next condition, which is:

@@

\subsection{$F$-term and the classical vacua}
	A full expansion of the Lagrangian $\mcal{L}$ (including $\mcal{K}$ and $\mcal{W}$) reveals that $F$ has no kinetic term and is quadratic in the action, thus it can be safely integrated out. The equation of motion is simply:
	\begin{equation}
		F^i = - g^{i\wbar{i}}
			\pdd{\wbar{i}} \wbar{\mcal{W}}
		+ \frac{1}{2}\,\Gamma^i_{jk} \psi^j \psi^k
	\end{equation}
	This gives a potential for the scalar component $\phi$:
	\begin{equation}
		V(\phi,\bar{\phi})
		= \norm{\pd\mcal{W}}^2
		= g^{i\wbar{j}}
			\,\pdd{i} \mcal{W}
			\,\pdd{\wbar{j}} \wbar{\mcal{W}}
		\xlongequal{\vev{\psi \psi} = 0}
		g_{i\wbar{j}} F^i \wbar{F}^{\wbar{j}}
		= \norm{F}^2
	\end{equation}
	Here we've used the fact that $\vev{\psi \psi} = 0$, so only the $\pd\mcal{W}$ term contributes to the VEV $\vev{F}$. Note that the non-zero fermion propagator is given by $\vev{\psi \bar{\psi}}$ instead.

	The classical vacua satisfy $\pd_i V = 0$. 
%	Spontaneous breaking of internal symmetry happens if we have $\vev{\phi} \ne 0$. 
	On the other hand, we see that $V\ge 0$ for a positive-definite metric $g_{i\wbar{j}}$, therefore if $V = 0$ we have $\pdd{i} V = 0$ and $\pdd{i} \mcal{W} = 0$. In this case we have SUSY vacua, i.e.~SUSY is unbroken.

	In summary,
	\begin{itemize}[noitemsep]
	\item Vacua: $
		\pdd{i} V
		= \pdd{i}\,\pqty\big{\norm{\pdd{i} \mcal{W}}^2}
		= 0
	$
	\item SUSY vacua: $\pdd{i} \mcal{W} = 0$, which implies $V = 0$ thus $\pdd{i} V = 0$. 
	\end{itemize}
	Spontaneous breaking of SUSY happens if $\pdd{i} V = 0$ while $V \ne 0$, namely we don't have a SUSY vacua. 	Fig.\,1.4 of \textcite{Terning:2006bq} is a nice summary of the situations. These backgrounds will come in handy in later sections.

@@

%	\vspace{\baselineskip}
	\pagebreak[3]
	\noindent%
	The argument of non-renormalization by Dine, Polchinski and Seiberg \cite{Seiberg:1993vc}:

@@

	\textit{Note:} in \cite{Seiberg:1993vc} Seiberg chose to call the non-renormalization in SUSY \textit{a violation of naturalness} in the conventional sense, since in the IR we see no global symmetry but we still have many vanishing amplitudes. But I believe it's okay to understand this as a new sense of naturalness, where the vanishing of amplitudes (or the rigid form of the potentials) is protected by supersymmetry and some ``hidden'' global symmetries (that are spontaneously broken in the IR).

\subsection{Why can we turn on the couplings?}
	We've argued that it's physically reasonable to turn on the coupling $\lambda$ and make it a dynamical field\footnote{
		I believe this is the so-called ``un-Higgs-ing'' procedure, and the unHiggsed field is called a ``spurion''. \\
		See \https{physicsforums.com/threads/spurion-symmetry.205417}.
	}. On the other hand, as pointed out by \textcite{Argyres:1996abc}, we can simply think of this as ``just a trick''\footnote{
		See also \https{physics.stackexchange.com/q/110926}. 
	}:

@@

	One concrete realization of this procedure for the $m\Phi^2$ term is given by \cite{Dine:1996ui}:
	\begin{equation}
	\begin{aligned}
		m\Phi^2
		\leadsto{}&
			M \pqty{
				\Psi - m
			}^2 + \Psi \Phi^2 \\
	\end{aligned}
	\end{equation}
	Here we've been cavalier about constant shifts of $\mcal{W}$, as they do not affect the physics\footnote{
		On the other hand, constant shifts of $V = \norm{\pd\mcal{W}}^2$ \textit{do} matter in SUSY theories, as they are related to spontaneous SUSY breaking; see \S2 and the following sections. 
	}. 
	Also, we are free to include a kinetic term for $\Psi$ in the K\"ahler potential so that it does look like a physical field. However, this does not matter much, as for $M \gg \Lambda_{\mrm{UV}}$, the $
		M \pqty{\Psi - m}^2
	$ term dominates and we always have $m \simeq \vev{\Psi}$. In the end the superpotential reduces back to $m\Phi^2$. Holomorphy of $\mcal{W}$ with respect to $m$ then follows from holomorphy with respect to $\Psi$.

@@

\section{Singularies from Integrating Out}
	\speaker{Yuan Zhong}\\
	\references{%
%	\begin{enumerate}[noitemsep,topsep=0pt]
%	\item
	\textcite{Argyres:1996abc}, \S8
%	\end{enumerate}
	}\vspace{.5\baselineskip}
